Integer-N PFD/CP-based PLL - System-Level simulation

### 2025-05-07 Examples/Example3_5_SystemPhaseNoiseCalculation/article/article.qmd
Almost finishing the example 3.5 and creating a script to extract the reports.

@@

display(Markdown(f"$$\\frac{{\\varphi_\\text{{no}}(s)}}{{\\varphi_\\text{{nI}}(s)}} = {latex_str}$$ {{#eq-filter-transfer-function}}"))
#display(Markdown(f"$$\\frac{{\\varphi_\\text{{no}}(s)}}{{\\varphi_\\text{{nI}}(s)}} = {latex_str_eq}$$ {{#eq-filter-transfer-function}}"))
```

>>>>

def format_raw(value, decimals=2):
    abs_value = abs(value)
    fmt = f".{decimals}f"

    return result

@@

display(Markdown(f"$$\\frac{{\\varphi_\\text{{no}}(s)}}{{\\varphi_\\text{{nI}}(s)}} = {latex_str}\\implies$$ {{#eq-filter-transfer-function}}"))
#display(Markdown(f"$$\\frac{{\\varphi_\\text{{no}}(s)}}{{\\varphi_\\text{{nI}}(s)}} = {latex_str_eq}$$ {{#eq-filter-transfer-function}}"))
```

import sympy as sp
from IPython.display import display, Markdown

# Converte para LaTeX
latex_str = sp.latex(H_subs)

display(Markdown(f"$$\\varphi_\\text{{no}}(s) = {latex_str}\\cdot {format_raw(phi_CP, 0)}$$ {{#eq-filter-transfer-function}}"))

Therefore, to plot phase noise in dBc/Hz, we take

$$
PN_{CP}=20\log\left(\varphi_\text{no}\right)
$$
